ML Estimation of Matrix t Distributions with Expectation Maximization

### 2016-12-11 paper.tex
Fix citations and add one reference

\documentclass[english,listof=totoc]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}

@@

\paragraph{Introduction}
Matrix--$t$ distributions have been applied to several predictive problems, such as spatial interpolation applied to the prediction of pollution concentration \cite{}, recommendation systems \cite{NIPS2007_3203}, and
...

@@

\bibliography{references}
\end{document}

>>>>

\documentclass[english,listof=totoc]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}\usepackage{mathtools}

@@

\paragraph{Introduction}
Matrix--$t$ distributions have been applied to several predictive
problems, such as spatial interpolation applied to the prediction of
pollution concentration \citep{KIBRIA2006785}, recommendation systems
\citep{NIPS2007_3203}, and ...

@@

\bibliographystyle{unsrtnat}
\bibliography{references}
\end{document}
